### 2020-03-06 thesis_template/2_RelatedWork/model/spark.tex
added experiment document

\section{Resilient Distributed Datasets}
\label{sec:history}
The major methods in Spark are Resilient Distributed Datasets (RDDs), a data structue that abstracts distributed memoy across different clusters. 
The immutable coarse-grained transformantion, spark-scheduler with lazy-evaluation, and memory management with cacheing achieve computation with fault-tolerance, 
fast execution, and moderate control on memory efficiency.

>>>>

\section{Resilient Distributed Datasets}
\label{sec:history}
The major methods in Spark are Resilient Distributed Datasets (RDDs), a data structue that abstracts distributed memoy across different clusters. 
The immutable coarse-grained transformantion, spark-scheduler with lazy-evaluation, and memory management with cacheing achieve computation with fault-tolerance, 
fast execution, and moderate control on memory efficiency \cite{DBLP:conf/nsdi/ZahariaCDDMMFSS12}.
